Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2023-03-09 src/docs_paper/paper.Rmd
Very long list of legends

>>>>

## List of legends

### S1 Text

#### Tables

* Table A: The multinomial regression models that we considered. Observation random effects $\theta_{ita}$, included in all models, are omitted from this table.
* Table B: Multinomial regression model performance, with the best performing model(s) according to each criterion shown as a square. For the CPO, higher values indicate better model performance for the CPO. For the 
DIC and WAIC, lower values indicate better model performance.
* Table C: The logistic regression models that were considered. \texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months.
* Table D: Logistic regression model performance. For the CPO, higher values indicate better model performance. For the DIC and WAIC, lower values indicate better model performance.

#### Figures

* Figure A: Multinomial regression model performance, with the best performing model(s) according to each criterion shown as a square. For the CPO, higher values indicate better model performance for the CPO. For the DIC and WAIC, lower values indicate better model performance.
* Figure B: Logistic regression model performance, with the best performing model(s) according to each criterion shown as a square.
* Figure C: Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected model.
* Figure D: Proportion of FSW by age group (including the age groups 30-34, 35-39, 40-44 and 45-49) as produced by our disaggregation procedure.

### S2 Text

#### Tables

* Table A: Prioritisation strata according to HIV incidence in the general population and behavioural risk.
* Table B: Commitments to be met for each intervention in terms of proportion of the prioritisation strata reached, where "-" represents no commitment.
* Table C: All of the surveys that we used in our analysis and their sample sizes, disaggregated by respondent age.
* Table D: All of that surveys that were excluded from our analysis.
* Table E: The numer of areas and analysis levels for each country that were used in our analysis.
* Table F: AIS, BAIS and DHS survey questions.
* Table G: PHIA survey questions.

#### Figures

* Figure A: Flowchart describing allocation of respondents to risk groups.
* Figure B: Illustration of our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.
* Figure C: Proportion of variance explained by each random effect (Sobol’ indices) when the multinomial regression model is fit to each country individually. In this setting, country-category random effects are not included in the model and year-category random effects are replaced by survey-category random effects (for countries with surveys in multiple years). Countries are ordered by the proportion of their variance which is explained by the area-category random effects.
* Figure D: The posterior density of national-level risk group proportions by age, illustrating the bi-modality of the cohabiting partner and non-regular and multiple partner(s) risk groups.
* Figure E: Comparison of modelled and direct national-level estimates in 1999-2018 in Botswana. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure F: Comparison of modelled and direct national-level estimates in 1999-2018 in Cameroon. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure G: Comparison of modelled and direct national-level estimates in 1999-2018 in Kenya. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure H: Comparison of modelled and direct national-level estimates in 1999-2018 in Lesotho. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure I: Comparison of modelled and direct national-level estimates in 1999-2018 in Mozambique. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure J: Comparison of modelled and direct national-level estimates in 1999-2018 in Malawi. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure K: Comparison of modelled and direct national-level estimates in 1999-2018 in Namibia. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure L: Comparison of modelled and direct national-level estimates in 1999-2018 in Eswatini. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure M: Comparison of modelled and direct national-level estimates in 1999-2018 in Tanzania. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure M: Comparison of modelled and direct national-level estimates in 1999-2018 in Uganda. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure O: Comparison of modelled and direct national-level estimates in 1999-2018 in South Africa. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure P: Comparison of modelled and direct national-level estimates in 1999-2018 in Zambia. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure Q: Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
* Figure R: District-level HIV prevalence for each of the risk groups in 2018 in Botswana.
* Figure S: District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.
* Figure T: District-level HIV prevalence for each of the risk groups in 2018 in Kenya.
* Figure U: District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.
* Figure V: District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.
* Figure W: District-level HIV prevalence for each of the risk groups in 2018 in Malawi.
* Figure X: District-level HIV prevalence for each of the risk groups in 2018 in Namibia.
* Figure Y: District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.
* Figure Z: District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.
* Figure AA: District-level HIV prevalence for each of the risk groups in 2018 in Uganda.
* Figure AB: District-level HIV prevalence for each of the risk groups in 2018 in South Africa.
* Figure AC: District-level HIV prevalence for each of the risk groups in 2018 in Zambia.
* Figure AD: District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.
* Figure AE: District-level HIV incidence for each of the risk groups in 2018 in Botswana.
* Figure AF: District-level HIV incidence for each of the risk groups in 2018 in Cameroon.
* Figure AG: District-level HIV incidence for each of the risk groups in 2018 in Kenya.
* Figure AH: District-level HIV incidence for each of the risk groups in 2018 in Lesotho.
* Figure AI: District-level HIV incidence for each of the risk groups in 2018 in Mozambique.
* Figure AJ: District-level HIV incidence for each of the risk groups in 2018 in Malawi.
* Figure AK: District-level HIV incidence for each of the risk groups in 2018 in Namibia.
* Figure AL: District-level HIV incidence for each of the risk groups in 2018 in Eswatini.
* Figure AM: District-level HIV incidence for each of the risk groups in 2018 in Tanzania.
* Figure AN: District-level HIV incidence for each of the risk groups in 2018 in Uganda.
* Figure AO: District-level HIV incidence for each of the risk groups in 2018 in South Africa.
* Figure AP: District-level HIV incidence for each of the risk groups in 2018 in Zambia.
* Figure AQ: District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.
* Figure AR: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.
* Figure AS: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.
* Figure AT: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.
* Figure AU: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.
* Figure AV: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.
* Figure AW: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.
* Figure AX: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.
* Figure AY: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.
* Figure AZ: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.
* Figure BA: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.
* Figure BB: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.
* Figure BC: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.
* Figure BD: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.

### 2023-03-09 src/docs_paper/tables-figures.Rmd
Journal formatting requirements
Very long list of legends

<!-- So that the tables and figures in this appendix are prefixed by "B." -->
\setcounter{table}{0}  
\renewcommand{\thetable}{B.\arabic{table}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{B.\arabic{figure}}

@@

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.png}}
\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.}
\label{fig:model-direct-benefits}
\end{figure}

>>>>

<!-- So that the tables and figures in this appendix are numbered alphabetically --->
\setcounter{table}{0}  
\renewcommand{\thetable}{\AlphAlph{\value{table}}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{\AlphAlph{\value{figure}}}

@@

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.png}}
\caption{Illustration of our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.}
\label{fig:model-direct-benefits}
\end{figure}
